Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated validatin defn

\begin{defn}
  The assurance that a product, service, or result meets the needs of the customer and other identified
  stakeholders \citep{project2017guide}.
\end{defn}

\begin{defn}
  Requirements validation examines the specification to ensure that all software
  requirements have been stated unambiguously; that inconsistencies, omissions,
  and errors have been detected and corrected; and that the work products
  conform to the standards established for the process, the project, and the
  product \citep{pressman2005software}.  \wss{Olu, is this definition
    originally from pressman, or should we track down the original source?}
\end{defn}

>>>>

\begin{defn}
  The assurance that a product, service, or result meets the needs of the customer and other identified
  stakeholders \citep{project2017guide}.
\end{defn}
\begin{defn}
	Software validation is the process of checking that the system conforms to its specification and
	that it meets the real needs of the users of the system \citep{sommerville}.

\end{defn}
\begin{defn}
	Software validation, where the software is checked to ensure that it is what the
	customer requires \citep{sommerville}.
\end{defn}
\begin{defn}
  Software validation is achieved through a series of tests that demonstrate conformity
  with requirements \citep{pressman2005software}.
\end{defn}

\begin{defn}
	Validation is concerned with establishing that the product fulfills its
	intended use \citep{Van vilet}.
\end{defn}
